Hourly Assimilation of Different Sources of Observations Including Satellite Radiances in a Mesoscale Convective System Case During RELAMPAGO campaign

### 2022-09-27 analysis/paper/paper_ana_20181122.tex
Paper aproved!!!

\documentclass[preprint, 3p, authoryear,review, 12pt]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%

@@

\usepackage{lineno} % add
  \linenumbers % turns line numbering on

@@

Particularly relevant for regional mesoscale DA systems in the region of interest is that South America is characterized by a limited number of conventional observations (i.e., radiosondes, surface weather stations) and operational networks that are not dense enough to capture mesoscale details. In this context, analyzing the potential impact of non-conventional sources of observations is essential to improve mesoscale numerical weather prediction (NWP) over South America using DA. There have been only a few published efforts on regional mesoscale DA, but they have all shown promising results \citep[e.g.][]{dillon2016, dillon2021, goncalvesdegoncalves2015}. In particular, \citet{dillon2021} assimilated high resolution surface weather station networks, GOES-16 atmospheric motion vectors (AMVs), and satellite temperature and moisture retrievals over central Argentina with positive impacts. Similar to \citet{gasperoni2018}, \citet{dillon2021} included private weather station networks which are not incorporated in the operational analysis. However, the impact of different observation types on the analysis quality has not been addressed.

The impact of non-conventional high spatial and temporal resolution observations, such as AMVs, has been investigated in the context of regional mesoscale DA. Many studies have focused on the impact of these observations on the prediction of tropical storms (e.g., \citet{wu2014}, \citet{cherubini2006}, and \citet{sawada2019}, and many others). Most of these studies reported an overall positive impact of the assimilation of AMVs for this type of storm. However, some works indicated mixed impacts (e.g. \citet{sawada2019} reported an improvement in the forecast of the track of the storm but a degradation in the forecast intensity). As stated in \citet{zhao2021, zhao2021a}, the impact of assimilating these data on high impact weather events associated with mid-latitude deep convection over land has received relatively less attention. \citet{zhao2021, zhao2021a} assimilated GOES-16 AMVs into a storm-scale three-dimensional variational DA system during three high impact weather events. They reported positive impacts of AMVs on the characterization of the storm environment and improved short range precipitation forecasts. \citet{otsuka2015} and \citet{mallick2020} found a slight improvement in the short-range precipitation forecast due to the storm-scale assimilation of high frequency AMVs.

@@

The main objective of this work is thus to contribute to the quantification and comparison of the impact of high resolution automatic weather stations, AMVs, and clear-sky satellite radiances, into a mesoscale, frequently-updated ensemble-based regional DA system. This is particularly important in the efforts to improve mesoscale numerical weather prediction (NWP) over South America where the conventional observation network is rather sparse and other sources of information could potentially fill certain gaps. In particular, this paper focuses on the impact in the context of a mid-latitude mesoscale convective system. To reach this goal, several DA experiments are conducted for a case study of a large Mesoscale Convective System (MCS) that developed over Southern South America during Nov 22-23, 2018 during the intense observation period (IOP) of the RELAMPAGO field campaign.

@@

\begin{itemize}
\item
  ERA5 hourly data on pressure levels from 1959 to present \citep{era5pressure}. The variables of interest (air temperature, humidity and wind) were interpolated to the model grid to compare them with the analysis of each experiment.
\item
  The Multi-Network Composite Highest Resolution Radiosonde Data \citep{sondeos} from the RELAMPAGO field campaign database consisting of high-resolution radiosondes launched from several locations during the IOPs along with the operational radiosondes. Only the soundings that did not enter the assimilation system were used for validation. The experiment period covers IOP missions 7 and 8, during which 74 radiosondes were launched in a small area near the center of the experimental domain (Figure \ref{fig:dominio}b).
\item
  The Satellite precipitation estimation IMERG Final Run with 0.01\(^{\circ}\) spatial resolution and 30 minutes temporal resolution \citep{huffman2018} was used as a reference state to validate the skill of 1-hour forecasts to represent the precipitation over the domain.
\item
  Radar observations are used to perform a qualitative and visual assessment of the convective features. The data comes from 9 radars located in the domain and is provided by the Argentine C-band Doppler dual-polarization weather radar network \citep{deelia2017} with a temporal frequency of 10 minutes. For this work, only the maximum reflectivity in the column (COLMAX) closest to the analysis time was used.
\end{itemize}

@@

The difference between ERA5 reanalyses \citep[`]{era5pressure} and the ensemble mean analyses are also compared in Figure \ref{fig:era5}, which supports Figures \ref{fig:TQ-diff} and \ref{fig:UV-diff}. Specifically, Figure \ref{fig:era5}a shows a warm bias in low levels (i.e.~CONV is warmer than ERA5) that decreases in Figure \ref{fig:era5}b when the AWS observations are assimilated. In the same direction, Figure \ref{fig:TQ-diff}a shows a negative difference between AWS and CONV meaning that the AWS observations are cooling the low levels. Comparing ERA5-RAD (Figure \ref{fig:era5}d), there is a small increase in the warm bias, associated with the warming produced by the radiance observations as shown in Figure \ref{fig:TQ-diff}c.~A similar effect can be observed for specific humidity, AWS observations partially correct the dry bias present in Figure \ref{fig:era5}e and the assimilation of radiance observations reduces the positive impact of AWS. The impact on the wind components is minor so only the meridional wind is included in Figures \ref{fig:era5}i-l, which show that the radiance observations are mainly responsible for the positive impact observed in the analysis by reducing the distance ERA5-RAD, particularly during the mature stage of the MCS. Overall, the adjustments due to assimilating radiance and AWS observations lead to an ensemble mean analyses closer to ERA5 reanalyses.

@@

\caption{Difference between ERA5 and the analysis ensemble mean experiments for the spatially averaged vertical profiles of air temperature (K, a--d), specific humidity (\(g\ Kg^{-1}\), e--h) and meridional wind (\(m\ s^{-1}\), i--l) calculated over the inner domain (red box in Figure \ref{fig:dominio}a) for each analysis cycle.}\label{fig:era5}
\end{figure*}

>>>>

\documentclass[final,5p,times,twocolumn,authoryear]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%

@@

\usepackage{lineno} % add

@@

Particularly relevant for regional mesoscale DA systems in the region of interest is that South America is characterized by a limited number of conventional observations (i.e., radiosondes, surface weather stations) and operational networks that are not dense enough to capture mesoscale details. In this context, analyzing the potential impact of non-conventional sources of observations is essential to improve mesoscale numerical weather prediction (NWP) over South America using DA. There have been only a few published efforts on regional mesoscale DA, but they have all shown promising results \citep[e.g.][]{dillon2016, dillon2021, goncalvesdegoncalves2015}. In particular, \citet{dillon2021} assimilated high resolution surface weather station networks, GOES-16 satellite-derived winds, and satellite temperature and moisture retrievals over central Argentina with positive impacts. Similar to \citet{gasperoni2018}, \citet{dillon2021} included private weather station networks which are not incorporated in the operational analysis. However, the impact of different observation types on the analysis quality has not been addressed.

The impact of non-conventional high spatial and temporal resolution observations, such as satellite-derived winds, has been investigated in the context of regional mesoscale DA. Many studies have focused on the impact of these observations on the prediction of tropical storms (e.g., \citet{wu2014}, \citet{cherubini2006}, and \citet{sawada2019}, and many others). Most of these studies reported an overall positive impact of the assimilation of satellite-derived winds for this type of storm. However, some works indicated mixed impacts (e.g. \citet{sawada2019} reported an improvement in the forecast of the track of the storm but a degradation in the forecast intensity). As stated in \citet{zhao2021, zhao2021a}, the impact of assimilating these data on high impact weather events associated with mid-latitude deep convection over land has received relatively less attention. \citet{zhao2021, zhao2021a} assimilated GOES-16 satellite-derived winds into a storm-scale three-dimensional variational DA system during three high impact weather events. They reported positive impacts of satellite-derived winds on the characterization of the storm environment and improved short range precipitation forecasts. \citet{otsuka2015} and \citet{mallick2020} found a slight improvement in the short-range precipitation forecast due to the storm-scale assimilation of high frequency satellite-derived winds.

@@

The main objective of this work is thus to contribute to the quantification and comparison of the impact of high resolution automatic weather stations, satellite-derived winds, and clear-sky satellite radiances, into a mesoscale, frequently-updated ensemble-based regional DA system. This is particularly important in the efforts to improve mesoscale numerical weather prediction (NWP) over South America where the conventional observation network is rather sparse and other sources of information could potentially fill certain gaps. In particular, this paper focuses on the impact in the context of a mid-latitude mesoscale convective system. To reach this goal, several DA experiments are conducted for a case study of a large Mesoscale Convective System (MCS) that developed over Southern South America during Nov 22-23, 2018 during the intense observation period (IOP) of the RELAMPAGO field campaign.

@@

\begin{itemize}
\item
  ERA5 hourly data on pressure levels from 1959 to present \citep{era5pressure}. The variables of interest (air temperature, humidity and wind) were interpolated to the model grid to compare them with the analysis of each experiment.
\item
  The Multi-Network Composite Highest Resolution Radiosonde Data \citep{sondeos} from the RELAMPAGO field campaign database consisting of high-resolution radiosondes launched from several locations during the IOPs along with the operational radiosondes. Only the soundings that did not enter the assimilation system were used for validation. The experiment period covers IOP missions 7 and 8, during which 74 radiosondes were launched in a small area near the center of the experimental domain (Figure \ref{fig:dominio}b).
\item
  The Satellite precipitation estimation IMERG Final Run with 0.1\(^{\circ}\) spatial resolution and 30 minutes temporal resolution \citep{huffman2018} was used as a reference state to validate the skill of 1-hour forecasts to represent the precipitation over the domain.
\item
  Radar observations are used to perform a qualitative and visual assessment of the convective features. The data comes from 9 radars located in the domain and is provided by the Argentine C-band Doppler dual-polarization weather radar network \citep{deelia2017} with a temporal frequency of 10 minutes. For this work, only the maximum reflectivity in the column (COLMAX) closest to the analysis time was used.
\end{itemize}

@@

The difference between the ensemble mean analyses and ERA5 \citep[`]{era5pressure} are also compared in Figure \ref{fig:era5}, which supports Figures \ref{fig:TQ-diff} and \ref{fig:UV-diff}. Specifically, Figure \ref{fig:era5}a shows a warm bias in low levels (i.e.~CONV is warmer than ERA5) that decreases in Figure \ref{fig:era5}b when the AWS observations are assimilated. In the same direction, Figure \ref{fig:TQ-diff}a shows a negative difference between AWS and CONV meaning that the AWS observations are cooling the low levels. Comparing with RAD-ERA5 (Figure \ref{fig:era5}d), there is a small increase in the warm bias, associated with the warming produced by the radiance observations as shown in Figure \ref{fig:TQ-diff}c.~A similar effect can be observed for specific humidity, AWS observations partially correct the dry bias present in Figure \ref{fig:era5}e and the assimilation of radiance observations reduces the positive impact of AWS. The impact on the wind components is minor and only the meridional wind is included in Figures \ref{fig:era5}i-l, which show that the radiance observations are mainly responsible for the positive impact observed in the analysis by reducing the distance RAD-ERA5, particularly during the mature stage of the MCS. Overall, the adjustments due to assimilating radiance and AWS observations lead to an ensemble mean analyses closer to ERA5.

@@

\caption{Difference between the analysis ensemble mean experiments and ERA5 for the spatially averaged vertical profiles of air temperature (K, a--d), specific humidity (\(g\ Kg^{-1}\), e--h) and meridional wind (\(m\ s^{-1}\), i--l) calculated over the inner domain (red box in Figure \ref{fig:dominio}a) for each analysis cycle.}\label{fig:era5}
\end{figure*}
